---
title: "Day 6 challange tet+/- coefficients from full/reduced Lasso model"
author: "Eivind G. Lund"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Rationale
Lasso regression is a common method for feature selection (doi: [10.1201/b17320](https://doi.org/10.1201/b17320)).
A weakness is that for highly correlated features, only one will be selected.
Similar methods such as elastic nets contain all correlated features with predictive power.
I chose the lasso method since we aim for a reduced set of features.

### Note
Markers from the old panel dominate the mixed panel. Their scores are identical when applying penalization since the same 
markers from the old panel are used in both cases.

## Analysis

```{r, echo=FALSE}
readd(lasso_penalty_performance_plot)
```

## Reduced model coefficients

### Mixed panel
```{r, echo=FALSE}
readd(lasso_coeffs)$mix$optimal %>% 
  kbl() %>% 
  kable_styling(full_width = FALSE)
```

### New panel
```{r, echo=FALSE}
readd(lasso_coeffs)$new$optimal %>% 
  kbl() %>% 
  kable_styling(full_width = FALSE)
```

### Old panel
```{r, echo=FALSE}
readd(lasso_coeffs)$old$optimal %>% 
  kbl() %>% 
  kable_styling(full_width = FALSE)
```

## Full model coefficients

### Mixed panel
```{r, echo=FALSE}
readd(lasso_coeffs)$mix$full %>% 
  kbl() %>% 
  kable_styling(full_width = FALSE)
```

### New panel
```{r, echo=FALSE}
readd(lasso_coeffs)$new$full %>% 
  kbl() %>% 
  kable_styling(full_width = FALSE)
```

### Old panel
```{r, echo=FALSE}
readd(lasso_coeffs)$old$full %>% 
  kbl() %>% 
  kable_styling(full_width = FALSE)
```

</details>
